You soon discover your first $\cancelto{\mathrm{opportunity}}{\mathrm{challenge}}$.
Archie purchased your workstation from government surplus.
Your keyboard is left over from early 2001 and is missing the letter \textit{\texttt{W}}!\footnote{In January 2001, when President Bill Clinton's staff left the White House so that President George~W. Bush's staff could move in, they removed the \textit{\texttt{W}} key from several keyboards as a prank.}
You decide to write an email requesting a new keyboard: \\
\\
\texttt{TO\tab Archie\nl} \\
\texttt{RE\tab I Need a Working Keyboard\nl} \\
\nl \\
\texttt{Please order a new keyboard for me. This one is broken.\nl } \\ \\
(Note: here, the \tab\ symbol represents the \texttt{TAB} character which is needed by the email program, and the \nl\ symbol represents a \texttt{NEWLINE} character.)

You quickly realize that you can't type this directly into your mail program because of the missing \textit{\texttt{W}} key.
So you decide to write a short program that will output the text that you want to send.
The code you would like to write is:

\begin{lstlisting}
#include <stdio.h>

int main() {
    printf("TO\tArchie\n");
    printf("RE\tI Need a Working Keyboard\n\n");
    printf("Please order a new keyboard for me. This one is broken.\n");
    return 0;
}
\end{lstlisting}

Of course, the \texttt{W} and the \texttt{w} are still a problem, but you realize you can insert those characters by using their ASCII values.\footnote{Use the ASCII table in the textbook or type \texttt{man ascii} in a terminal window.}
For example,

\lstinline{printf("Hello World!\n");} \\
can be replaced with

\lstinline{printf("%s%c%s\n", "Hello ", ..., "orld!");} \\
replacing \dots\ with the ASCII value for \texttt{W}.
Recall that the first argument for \function{printf()} is a \textit{format string}: \texttt{\%s} specifies that a string should be placed at that position in the output, and \texttt{\%c} specifies that a character should be placed at that position in the output.

As you open your editor, the \textit{\texttt{\textbackslash}} key falls off the keyboard, preventing you from typing \texttt{\textbackslash t} and \texttt{\textbackslash n}.

Edit \texttt{problem1.c} so that it produces the specified output without using the W key or the backslash key.
Build the executable with the command: \texttt{make keyboardlab1} -- be sure to fix both errors and warnings.

You can double-check that you aren't using the W key or the backslash key by running the constraint-checking shell script: \\
\texttt{./constraint-check.sh} \\
(If you get a ``\texttt{Permission denied}'' error message, then run the command \\
\texttt{chmod +x constraint-check.sh} \\
and then run the shell script.)

You can check that your program has the correct output with this command: \\
\texttt{./keyboardlab1 | diff - problem1oracle}
