When you have completed this assignment, upload \textit{PollingLab.ino} to
\filesubmission.

This assignment is worth 40 points. \\

Rubric:
\begin{description}
\rubricitem{1}{The inputs are debounced in software in a fashion that permits other inputs to be handled as they arrive.}
\item[Memory-Mapped Input/Output]
\rubricitem{6}{The simple input/output functions are correctly implemented. (2 points for \function{xx_switch_in_xx_position()} functions; 2 points for \function{xx_button_is_pressed()} functions; 2 points for \function{set_xx_led()} funcitons)}
\rubricitem{8}{The \function{get_keypress()} function is correctly implemented.}
\rubricitem{8}{The \function{send_halfbyte()} function is correctly implemented.}
\item[Implementing a Simple System using Polling]
\rubricitem{2}{Left justified mode and right justified mode are implemented correctly.}
\rubricitem{2}{Decimal and hexadecimal number bases are implemented correctly.}
\rubricitem{2}{The LED illumination occurs as specified.}\rubricitem{2}{The first digit of a number is displayed in the correct position, making a blank display no longer blank, in accordance with requirements~\ref{spec:decimalExplained}, \ref{spec:hexadecimalExplained}, and \ref{spec:initialKeyPress}.}
\rubricitem{2}{Subsequent digits update the number in accordance with requirements~\ref{spec:decimalExplained}, \ref{spec:hexadecimalExplained}, and \ref{spec:BuildingValue}.}
\rubricitem{2}{The left pushbutton negates the number's value (\textonehalf\ point for each of: negating positive decimal values, negating negative decimal values, negating positive hexadecimal values, negating negative hexadecimal values)}
\rubricitem{2}{Detects and displays correct message when the number being built is too big. (\textonequarter\ point for detecting too-big numbers for each of: positive decimal numbers, negative decimal numbers, positive hexadecimal numbers, negative hexadecimal numbers; \textonequarter\ point for no false detections among each of: decimal numbers, hexadecimal numbers; \textonehalf\ point for printing the correct message)}
\rubricitem{2}{The right pushbutton causes a copy of the number to be displayed on the bottom row for one second, after which the display clears.}
\rubricitem{1}{A button press or a key press that lasts fewer than 500ms is treated as a single press.}
\bonusitem{2}{Get assignment checked-off by TA or professor during office hours before it is due. (You cannot get both bonuses.)}
\bonusitem{1}{Get assignment checked-off by TA at \textit{start} of your scheduled lab immediately after it is due. (Your code must be uploaded to \filesubmission\ \textit{before} it is due. You cannot get both bonuses.)}
\item[Penalties]
\penaltyitem{22}{The memory-mapped input/output functions' implementations violate one or more constraints identified in Section~\ref{sec:Constraints}.}
\penaltyitem{17}{The simple system's implementation violates one or more constraints identified in Section~\ref{sec:Constraints}.}
\spaghetticodepenalties{1}
\end{description}