As is the case for integer arithmetic, the heavy-lifting for addition and subtraction is handled solely by the \function{add()} function.
The \function{subtract()} function is already implemented in terms of \function{add} and the \function{negate()} function.

\subsection{Add}

The \function{add()} stub identifies a handful of special cases that you can easily handle.
After the guard clauses are handled, your task is to implement addition for two finite, non-zero numbers.

Recall that for any number base, $b$, adding two floating point values $m_1 \times b^{e_1} + m_2 \times b^{e_2}$ is simplified when $e_1 = e_2$.

Start by adjusting one of the denormalized operands so that the two denormalized operands have the same exponent.
It is acceptable for the least significant bit (or even several less significant bits) to be truncated;
however, \textit{you must take care that the most significant bit does not get truncated}!

You have two options to get the exponents to match, both of which are well-supported by the Unnormal functions (see Section~\ref{subsec:unnormal}):
\begin{enumerate}
    \item First place each operand's significand entirely in the integer portion.
        Then whichever operand has the is greater exponent, shift that operand's significand to the left (decreasing the exponent, moving the binary point to the right) until the exponents match or until one more shift would make addition unreliable.
        If the exponents still do not match, then shift the other operand's significand to the right (increasing the exponent, moving the binary point to the left) until the exponents match. \\ \textit{Or,}
    \item Determine the difference between the operands' exponents and use the appropriate function to set one of the operands' exponent to match the other's.
        \textit{Do \textbf{not} decrease either exponent by more than 62} or you run the risk of making addition unreliable and possibly causing the significand to overflow.
        If you increase only one exponent, then you can increase it as much as you need to -- any bits lost to underflow will not affect the value after rounding.\footnote{
            Prove the professor wrong bonus: if a counterexample exists, the first student to bring it to my attention will receive a 10-point bonus on this assignment.
        }$^{,}$\footnote{
            This bonus has not yet been claimed.
        }
\end{enumerate}

You can now add the two values using integer arithmetic.
\ifbool{offerdecompositionhints}{
    \textit{Hint:} if the two operands have the same sign, add the significands;
    if the two operands have different signs, subtract the significands.
}{}

\begin{enumerate}
    \item If you selected the first option above, you need only to add the integer portions, setting the fraction portion to 0.
        If you shifted an operand's significand to the right only after the other operand is shifted as far to the left as is safe to do so, then any bits that were shifted into the fraction would be lost to rounding anyway.\footnote{
            Prove the professor wrong bonus: if a counterexample exists, the first student to bring it to my attention will receive a 10-point bonus on this assignment.
        }$^{,}$\footnote{
            This bonus has not yet been claimed.
        }
    \item If you selected the second option above, you will need to add both the integer and the fraction portions,
        and you will need to check whether the fraction carries into (or borrows from) the integer portion;
        if so, you will need to add 1 to (or subtract 1 from) the integer to account for this.
\end{enumerate}

\subsection{Negate}

The \function{negate()} function is simple: it only needs to change the number's sign bit.

\subsubsection*{Check Your Work}

When you run \texttt{\textbf{\textit{./floatlab}}}, you can enter a two-operand expression, such as addition and subtraction.
As before, if an operand is prepended with \texttt{\textbf{\textit{0x}}} then the parser will treat it as a bit vector;
otherwise, the parser will treat it as a floating point value.

\begin{verbatim}
Enter a value, a two-operand arithmetic expression,
    "denormalize <value>", "renormalize <value>",
    or "quit": 1 + 2
0x3f800000	+1.0000,0000,0000,0000,0000,000_{2} x 2^{0}
+
0x40000000	+1.0000,0000,0000,0000,0000,000_{2} x 2^{1}
expected: 3.0000000000_{10}	0x40400000	+1.1000,0000,0000,0000,0000,000_{2} x 2^{1}
actual:   3.0000000000_{10}	0x40400000	+1.1000,0000,0000,0000,0000,000_{2} x 2^{1}
\end{verbatim}

Be sure to check:
\begin{itemize}
    \item The identity and commutative properties
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{5 + 0}}}
        \item[] \texttt{\textbf{\textit{2 + 3}}}
        \item[] \texttt{\textbf{\textit{3 + 2}}}
    \end{itemize}
    \item Cases in which the exponent will be greater than that of either operand
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{3 + 3}}}
    \end{itemize}
    \item Fractional operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{.4 + .04}}}
    \end{itemize}
    \item Not only the use of negative operands, but also subtraction
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{-5 + 2}}}
        \item[] \texttt{\textbf{\textit{2 - 5}}}
        \item[] \texttt{\textbf{\textit{3 - -3}}}
    \end{itemize}
    \item Numbers both great and small
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{1.65e35 + 2.39e29}}}
        \item[] \texttt{\textbf{\textit{1.65e-39 + 2.39e-33}}}
    \end{itemize}
    \item A sufficiently-large sum overflows to infinity
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x7F7FFFFF + 0x73800000}}}
    \end{itemize}
    \item A sufficiently-small difference between normal numbers underflows to subnormal numbers
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x01000000 - 0x00C00000}}}
    \end{itemize}
    \item A number subtracted from itself produces zero:
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x00000001 - 0x00000001}}}
    \end{itemize}
    \item NaN and Infinity are ``sticky'' (except for $\infty - \infty$)
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{nan + 1}}}
        \item[] \texttt{\textbf{\textit{inf - 0x7F7FFFFF}}}
        \item[] \texttt{\textbf{\textit{inf - inf}}}
    \end{itemize}
\end{itemize}

\textit{Note: For the \function{add()} function, we will not deduct points if you have the wrong sign for Zero or for Not-a-Number} because the appropriate sign is usually indeterminate
(There are two cases where the sign can be determined; can you discover which cases those are?)

\subsubsection*{Rounding}

You can now check the rounding code in your \function{normalize()} implementation.

\begin{itemize}
    \item When the rounded-off portion is less than halfway, you always round down
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x40000000 + 0x33FFFFFF}}}
        \item[] \texttt{\textbf{\textit{0x40000001 + 0x33FFFFFF}}}
    \end{itemize}
    \item When the rounded-off portion is more than halfway, you always round up
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x40000000 + 0x34000001}}}
        \item[] \texttt{\textbf{\textit{0x40000001 + 0x34000001}}}
    \end{itemize}
    \item When the rounded-off portion is exactly halfway, you round to the nearest-even
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x40000000 + 0x34000000}}}
        \item[] \texttt{\textbf{\textit{0x40000001 + 0x34000000}}}
    \end{itemize}
    \item Sometimes rounding can carry all the way to the integer portion, causing the exponent to change
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x407FFFFF + 0x34000000}}}
    \end{itemize}
\end{itemize}