Recall that for any number base, $b$, multiplying two floating point values $m_1 \times b^{e_1} + m_2 \times b^{e_2}$ produces $m_1 \cdot m_2 \times b^{e_1 + e_2}$.
Similarly, dividing the two floating point values yields $\frac{m_1}{m_2} \times b^{e_1 - e_2}$.

\subsection{Multiply}

The \function{multiply()} stub identifies a handful of special cases that you can easily handle.
After the guard clauses are handled, your task is to implement multiplication for two finite, non-zero numbers.

While you have the option of performing integer multiplication without adjusting the denormalized operands (it would require only a little modification of your code from IntegerLab), we recommend that you adjust the denormalized operands so that you can use C's integer multiplication operator.
Adjust the denormalized operands such that their significands are both fully in the integer portion.
Because you do not need to give the two operands the same exponent, you do not need to worry about any further adjustment.
Multiply the two operands together using integer arithmetic.

\subsubsection*{Check Your Work}

Be sure to check:
\begin{itemize}
    \item The identity, zero, and commutative properties
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{5 * 1}}}
        \item[] \texttt{\textbf{\textit{5 * 0}}}
        \item[] \texttt{\textbf{\textit{2 * 3}}}
        \item[] \texttt{\textbf{\textit{3 * 2}}}
    \end{itemize}
    \item Integer operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{75 * 7}}}
        \item[] \texttt{\textbf{\textit{5 * 25}}}
    \end{itemize}
    \item Fractional operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{.75 * 7}}}
        \item[] \texttt{\textbf{\textit{5 * .25}}}
    \end{itemize}
    \item Negative operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{-5 * 2}}}
        \item[] \texttt{\textbf{\textit{5 * -2}}}
        \item[] \texttt{\textbf{\textit{-5 * -2}}}
        \item[] \texttt{\textbf{\textit{5 * -0}}}
    \end{itemize}
    \item Numbers both great and small
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{1.65e25 * 2.39e11}}}
        \item[] \texttt{\textbf{\textit{1.65e-25 * 2.39e-11}}}
        \item[] \texttt{\textbf{\textit{1e-30 * 1e-8}}}
        \item[] \texttt{\textbf{\textit{2e30 * 2e-30}}}
    \end{itemize}
    \item A sufficiently-large product overflows to infinity
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x7E000000 * 0x41000000}}}
    \end{itemize}
    \item A sufficiently-small product underflows to zero
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{0x3C800000 * 0x00000020}}}
    \end{itemize}
    \item NaN and Infinity are ``sticky'' (except for $\infty \times 0$)
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{nan * 1}}}
        \item[] \texttt{\textbf{\textit{inf * 2}}}
        \item[] \texttt{\textbf{\textit{inf * 0}}}
    \end{itemize}
\end{itemize}

\textit{Note}: For the \function{multiply()} function, we will not deduct points if you have the wrong sign for Not-a-Number.
\textit{We will, however, deduct points if you have the wrong sign for Zero.}

\subsection{Divide}

Implementing the \function{divide()} function is very similar to implementing \function{multiply()} with three exceptions:

\begin{itemize}
    \item There are different special cases
    \item You subtract the exponents and divide the significands
    \item Integer division is insufficient
\end{itemize}

We will limit our implementation of \function{divide()} to the special cases and to cases in which the dividend's significand is a multiple of the divisor's significand.
In this limited implementation, integer division is sufficient.

\subsubsection*{Check Your Work}

Be sure to check:
\begin{itemize}
    \item The identity property
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{5 / 1}}}
    \end{itemize}
    \item Integer operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{75 / 4}}}
    \end{itemize}
    \item Fractional operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{.75 / 4}}}
        \item[] \texttt{\textbf{\textit{5 / .25}}}
        \item[] \texttt{\textbf{\textit{.75 / .25}}}
    \end{itemize}
    \item Negative operands
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{-4 / 2}}}
        \item[] \texttt{\textbf{\textit{4 / -2}}}
        \item[] \texttt{\textbf{\textit{-4 / -2}}}
    \end{itemize}
    \item Divisors that require more than one 1 in the significand (but the dividend's significand is still a multiple of the divisor's significand)
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{30 / 5}}}
        \item[] \texttt{\textbf{\textit{25 / 0x3F200000}}}
        \item[] \texttt{\textbf{\textit{0x3F480000 / 5}}}
    \end{itemize}
    \item The special cases
    \begin{itemize}
        \item[] \texttt{\textbf{\textit{nan / 2}}}
        \item[] \texttt{\textbf{\textit{2 / nan}}}
        \item[] \texttt{\textbf{\textit{inf / 2}}}
        \item[] \texttt{\textbf{\textit{0 / 2}}}
        \item[] \texttt{\textbf{\textit{2 / inf}}}
        \item[] \texttt{\textbf{\textit{2 / 0}}}
        \item[] \texttt{\textbf{\textit{inf / inf}}}
        \item[] \texttt{\textbf{\textit{0 / 0}}}
    \end{itemize}
\end{itemize}

\textit{Note}: For the \function{divide()} function, we will not deduct points if you have the wrong sign for Not-a-Number.
\textit{We will, however, deduct points if you have the wrong sign for Zero.}