\transitiontwo\
As you fasten a Scrabble tile in place for the \textit{\texttt{\missingKey}}, more keys fall off, denying you the use of \textit{\texttt{+}}, \textit{\texttt{-}}, \textit{\texttt{/}}, \textit{\texttt{\%}}, \textit{\texttt{5}}, and \textit{\texttt{b}}.
You cannot get any more \adhesive, so you sit down to your next programming tasks without those keys.

\begin{description}
    \checkoffitem{Edit \texttt{problem3.c} so that
        \begin{itemize}
            \item \function{is_even()} returns 1 if the number is even (that is, divisible by 2) and 0 if the number is odd
            \item \function{produce_multiple_of_ten()} will always output a multiple of 10 following a specific formula: if a number is even then divide it by 2;
            otherwise, subtract 1 from the number and multiply the difference by 5 (for example, an input of 7 yields 30 because $(7-1) \times 5 = 30$);
            repeat until the last decimal digit is 0.
        \end{itemize}
        These numbers are guaranteed to be non-negative.
        You may not use addition (+), subtraction (-), division (/), nor modulo (\%).
        You also may not use the number 5 nor the letter b.
        (Exceptions: you \textit{may} use the forward-slash (/) for comments, and the percent-sign (\%) that is already present in the \function{sprintf()} calls' format strings is allowed)}
\end{description}

Hints:
\begin{itemize}
    \item Following the weighted-sum technique to convert between binary and decimal (or by examining the textbook's Table~2.1), you will note that \\ \colorbox{yellow}{all even numbers have a 0 as their least significant bit}, and \\ \colorbox{yellow}{all odd numbers have a 1 as their least significant bit}
    \item Less obvious is that you can \\ \colorbox{yellow}{subtract 1 from an odd number by changing its least significant bit to a 0}
    \item As we will cover in Chapter~3, you can \\ \colorbox{yellow}{halve a number by shifting its bits to the right by one}
    \item You can create an integer by \\ \colorbox{yellow}{producing its bit pattern through a series of bit operations}
\end{itemize}

\textit{Note: } \function{is_even()} can be implemented with as little as one line of code;
you might find a 1-line implementation easier to achieve.

\begin{description}
    \checkoffitem{Build the executable with the command: \texttt{make}.
        Be sure to fix both errors and warnings.}
    \checkoffitem{Run the executable with the command: \texttt{./keyboardlab} and select option 3 (``check problem 3'').
        You will be prompted to enter a number.
        The program will then report whether or not it is even, and it will print the generated multiple of ten.}
\end{description}
Here are some test values you might try:

\begin{center}
    \begin{tabular}{cc}
        input   & multiple of ten \\ \hline
        7       & 30    \\
        56      & 30    \\
        57      & 280   \\
        58      & 140   \\
        300     & 300   \\
        301     & 1500  \\
        302     & 750   \\
    \end{tabular}
\end{center}

\textcolor{red}{
You can double-check that you aren't using disallowed keys by running the constraint-checking Python script: \\
\texttt{python constraint-check.py keyboardlab3.json}
}

The \function{is_even()} function is worth four points, two for correctly determining that an integer is even and  two for correctly determining that an integer is odd.
Partial credit is available for determining that a character is even but returning a non-zero value other than 1.
You will receive no credit if you simply hard-code a return value.

The \function{produce_multiple_of_ten()} function is worth four points, one each for: assigning the value 5 to the variable \lstinline{five}, dividing an even number by 2, subtracting 1 from an odd number, and having the correct functionality.
